Automated topic naming to support analysis of software maintenance activities

### 2010-08-17 icse/icse2011.tex
abram's remunging of the intro (which actually keeps most of the original content)

The act of developing software generates many artifacts, including source code, bug reports, commit messages, and test cases. It does not take long for a software project to grow to a point where keeping track of these artifacts exceeds easy comprehension. For these projects, developers interact with abstractions of these artifacts, rather than the artifact itself. Such abstractions include project dashboards~\cite{kersten2005mylar}, tags~\cite{treude2010}, and complexity metrics \cite{mccabe1976complexity}.

Developers do more than merely observe these abstractions, however. They must also use them to assess progress and work with colleagues. To have meaningful discussions about how software development is progressing, we must be able to devise appropriate labels for our development artifacts. Such labels can be used to compare progress or understand how well a project is meeting requirements. These labels then become the topics for development conversations (such as the stream of commentary on a bug report). One way to identify topics is to use the artifacts themselves to derive them. 
\todo[inline]{it should be labels for topics not artifacts, I think the artifact part is almost secondary and the topic stuff is really what is up. Topics are used below and it isn't even clear what they are or what we're talking about. Naming is important but lets tell the reader what is being named first.}

Deriving such topics is difficult. Topics have to be identified by interpreting the prevalent words in a word distribution and by inspecting related documents. This is impractical when one has to handle more than one hundred different topics. To scale to meaningfully sized projects, we require automatic assistance to determine the topic label.
\todo[inline]{Readers still don't know what topics are or what the point is yet..}

@@

In this paper, we describe \textbf{Nomen}, which is a tool for \emph{labelled topic extraction}. \textbf{Nomen} addresses two gaps in the topic mining literature:
\begin{enumerate}
  \item Topic mining of software has been limited to one project at a time. This is because traditional topic mining techniques are specific to a particular data-set. \textbf{Nomen} allows for comparisons \textit{between} projects. 
  \item Topic modeling creates bags of words that require interpretation by the user to assign meaning. Like (1), this means
that it is difficult to discuss results independent of the project context. Our technique automatically assigns labels agnostic of project.
\end{enumerate}

@@

\todo[inline]{Topics are poorly defined by this point and since we're building on research which didn't DO this, we should mention that research. Previous work probably should go here.}

>>>>

When a developer addresses a topic of development, such as a requirement, maintenance, bug fixing, tests or other software engineering tasks, they often produce or modify multiple development artifacts.
%
These development artifacts include: source code, bug reports, revisions to source code, and even test cases. 
%
Topics that are addressed are sometimes not immediately resolved, some topics recur across time, yet others are only dealt with briefly.
%
The goal of concept location and topic analysis research is to semi-automatically recover some of these topics, and the related software artifacts.
% get neil's data mining point in there
The results of topic analysis and concept location are often very project specific, and not globally generalizable.
% get the interpretation aspect
As well much of the current research stops short of interpreting the purpose of the topic. That is, topics extracted are usually manually named and labelled by readers.
% 
Thus in this paper, we propose a method of interpreting and labelling some topics, and their related artifacts, that is generalizable and relevant to multiple projects.

% % a rough sketch
% The size of these artifacts is cumbersome for a developer or stakeholder to comprehend, thus they often have to be ``chunked'', grouped, modularized, organized and finally labelled.
% Even more difficult is to pull together tangible trails or interests that pervade these artifacts.
% These interests or topics are only really visible by analyzing multiple artifacts.
% Other researchers have focused on extracting these topics from development artifacts, but often their approach leaves the organization or the labelling step to the user.
% What we propose is to 
% In this paper, we seek to automatically extract these interests, or topics that link artifacts such as source control commits and label them.

% % Read for SE Data Mining
% % Read for Topic Naming
% % Read for previous research DID NOT
% % thoughts, what does this do what are we introducing
% % these abstractions ... how to link them

% The act of developing software generates many artifacts, including source code, bug reports, commit messages, and test cases. 
% It does not take long for a software project to grow to a point where keeping track of these artifacts exceeds easy comprehension. 
% For these projects, developers interact with abstractions of these artifacts, rather than the artifact itself. Such abstractions include project dashboards~\cite{kersten2005mylar}, tags~\cite{treude2010}, and complexity metrics \cite{mccabe1976complexity}.

% Developers do more than merely observe these abstractions, however. They must also use them to assess progress and work with colleagues. To have meaningful discussions about how software development is progressing, we must be able to devise appropriate labels for our development artifacts. Such labels can be used to compare progress or understand how well a project is meeting requirements. These labels then become the topics for development conversations (such as the stream of commentary on a bug report). One way to identify topics is to use the artifacts themselves to derive them. 
% \todo[inline]{it should be labels for topics not artifacts, I think the artifact part is almost secondary and the topic stuff is really what is up. Topics are used below and it isn't even clear what they are or what we're talking about. Naming is important but lets tell the reader what is being named first.}

% topics are numerous?
Deriving such topics is difficult. 
Raw topics from topic analysis are represented as unlabelled context-less word-lists or word distributions.
Topics have to be identified by interpreting the prevalent words in a word distribution and by inspecting related documents. 
This manual approach is impractical when one has to handle more than one hundred different topics. 
To scale to meaningfully sized projects, we require automatic assistance to determine the topic label.

% why are topics useful
Often developers interact with abstractions of these artifacts, rather than the artifact itself. 
Topics are a valuable and automatically extractable abstraction of software artifacts.
It abstracts these artifacts by their purpose or topic rather than their concrete representation.
The topic of development is relevant because it shows anyone inspecting these topics what were the distinct issues or topics facing development at a certain time.
Such abstractions include project dashboards~\cite{kersten2005mylar}, tags~\cite{treude2010}, and complexity metrics \cite{mccabe1976complexity}.

@@

% harp on data mining more
In general the data mining of software artifacts tends to be very project specific, yet NFRs are not. 
NFRs are prevalent in almost all software systems.
Thus our method of generalizing the data mining of these software artifacts is use the domain knowledge of software engineering, specifically NFRs. 
This allows us to data mine software systems with the intention of comparing their NFR related development topics.
% in order to achieve generalizable, cross project data mining results.

%% RESEARCH DIDNT DO THIS AND WE ARE TOTALLY AWESOME AND WE DID
% it is ok to repeat this here because it is clear and bullet pointed and the reviewers wont have any bloody excuse to not see it
In this paper, we describe \textbf{Nomen}, which is a tool for \emph{labelled topic extraction}. \textbf{Nomen} addresses two gaps in the topic mining literature:
\begin{enumerate}
  \item Topic mining of software has been limited to one project at a time. This is because traditional topic mining techniques are specific to a particular data-set. \textbf{Nomen} allows for comparisons \textit{between} projects. 
  \item Topic modeling creates word lists that require interpretation by the user to assign meaning. Like (1), this means
that it is difficult to discuss results independent of the project context. Our technique automatically assigns labels agnostic of project.
\end{enumerate}

@@

%\todo[inline]{Topics are poorly defined by this point and since we're building on research which didn't DO this, we should mention that research. Previous work probably should go here.}
